---
title: "Documentation"
author: "Oriane Pierrès, Philipp Bosch, Lukas Birkenmaier"
date: 12.05.2021
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# CitiesRopen

This packages provides an easy and accessible tool to access data from the Open Data Portal of Constance. Data is retrieved using the [DKAN API](https://www.offenedaten-koeln.de/blog/dkan-api-howto)

## Getting Started

You can install the package directly from Github using the `install_github` function from the `devtools` package as shown below. Please make sure, that you have the `devtools` package locally installed on your machine before starting the download. 

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("PhilippMartinBosch/CitiesRopen")
```

## Structure

The package provides to major functions, which allow complete access 

### Use Cases


```{r, eval=FALSE}
CitiesRopen::show_data(tag = "Politik und Wahlen", format = "csv") %>% 
  CitiesRopen::get_data()
```




`
